---
title: "Untitled"
author: "moi"
date: "March 1, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r tutorial, echo = TRUE}
#les packages (à installer si non disponible)
library(raster)
library(rasterVis)
#lire les donnees
#preciser le chemin !
chl<-stack("chl")
#plot
plot(chl)
#une moyenne
chlmean<-mean(chl,na.rm=T)
#un joli graphique
levelplot(chlmean,margin=F,zscale=T,contour=T,par.settings=
	      viridisTheme,main="Concentration en chlorophylle a\nmoyenne 2010-2017")
#une extraction spatiale dans le sud-ouest
sudouest<-extent(-2,-1,44,45)
chlsmall<-crop(chl,sudouest)
#plot pour verifier
plot(chlsmall)
#une serie temporelle moyenne
#chlts<-extract(chlsmall,sudouest,method="bilinear",fun=mean,na.rm=T)
chlts<-cellStats(chlsmall,stat="mean",na.rm=T)
#vecteur temporel
temps<-strptime(gsub("X","",names(chlts)),"%Y.%m.%d")
plot(temps,chlts,type="l")

#une fonction pour calculer le P90
p90<-function(a,na.rm=T){return(quantile(a,probs=.9,na.rm=T))}
#une carte du P90 sur toute la série
chlsmallp90<-stackApply(chlsmall,rep(1,nlayers(chlsmall)),p90)
#choli plot
levelplot(chlsmallp90,margin=F,zscale=T,contour=T,par.settings=
	      viridisTheme,main="P90 2010-2017")
levelplot(chlsmallp90,margin=F,zscale=F,contour=T,par.settings=
	      viridisTheme,main="P90 2010-2017")
#ratio
chlsmallp90ratio<-3.33/chlsmallp90
#fonction de classif des intervalles
etat<-function(a){1+findInterval(a,c(0.08,0.17,0.33,0.6),rightmost.closed=T)} 	
chlsmallp90eqr<-calc(chlsmallp90ratio,etat)
		   
levelplot(chlsmallp90eqr,margin=F,zscale=F,contour=T,par.settings=
	      viridisTheme,main="P90 2010-2017")
#ou
plot(chlsmallp90eqr)




```

## Slide with Plot

Some text

```{r pressure}
plot(rnorm(100))
```

